---
title: "CORRELATION_ANALYSIS"
#author: "CHENRUJIE"
#date: "2022年7月9日"
output: 
  html_document: 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
globalWD <- file.path("~/PRO80")
globalWD.DATA <- file.path(globalWD, "DATA")

desiredIndex_1 <- "CU0"
desiredIndex_2 <- "RB0"
desiredIndex_3 <- "I0"

wd_Start = "2022-05-15"

# Libraries.--------------------------------------------------------------------
library(readr)
library(timeDate)
library(timeSeries)
```

I now become understand the importance of identifying the correlations between price changes among the commodities to make the a box out of it at either 11 or 7 numbers. Now let me take a step back to look at the commodities price changes. 

# Reading the Daily Trading Data.

```{r Loading Daily Trading Data, paged.print=FALSE}
## Loading All Trading Data pre processing.=====================================
TD_All <- read_csv(file.path(globalWD, "DEEPLEARN/TD_All.csv"), col_types = cols(X1 = col_date(format = "%Y-%m-%d")))
TD_All.df <- as.data.frame(TD_All,  stringsAsFactors = FALSE)
colnames(TD_All.df)[1] <- c("Date")

# Let's derive the hpfc of all Trading Data.
CMS_Daily.index <- read_csv(file.path(globalWD, "DailyTDs/ref_TD.csv")) 
CMS_Daily.index.df <- as.data.frame(CMS_Daily.index, stringsAsFactors = FALSE)
CMS_Daily.df <- TD_All.df[, c("Date", paste0(CMS_Daily.index.df[1, ], "Close"))]
CMS_Daily.ts <- timeSeries(CMS_Daily.df[, -1], charvec = CMS_Daily.df$Date)

print('DONE!')
```

# Generate Log Return

```{r Generate Log Return With Desired Index Ordering}

# Function to generate desired index order.
desiredOrder <- function(ref_index, desiredIndex = "RB0"){
  x <- ref_index[1, ] == desiredIndex
  x <- order(x, decreasing = TRUE)
  return_ref_index <- ref_index[x]
  return(return_ref_index)
}

# Function to generate log return.
generateLogr <- function(dataset_ts, order){
  # Generate log return of basket 1
  basketDaily_ts <- dataset_ts[, c(paste0(order, "Close"))]
  # Shrinking into window time.
  basketDaily_ts <- basketDaily_ts[rownames(basketDaily_ts)>=wd_Start, ]
  basketDaily_ts <- timeSeries::na.omit(basketDaily_ts)
  # Generate log returns.
  basketDailylogr_ts <- log(basketDaily_ts/lag(basketDaily_ts, 1))
  basketDailylogr_ts <- timeSeries::na.omit(basketDailylogr_ts)
  colnames(basketDailylogr_ts) <- order
  return(basketDailylogr_ts)
}
# Generate log returns.---------------------------------------------------------
# Generate log return of basket 1
basketindex_Order_1 <- desiredOrder(CMS_Daily.index.df[1, ], desiredIndex_1)
basketDailylogr_ts_1 <- generateLogr(CMS_Daily.ts, basketindex_Order_1)

basketindex_Order_2 <- desiredOrder(CMS_Daily.index.df[1, ], desiredIndex_2)
basketDailylogr_ts_2 <- generateLogr(CMS_Daily.ts, basketindex_Order_2)

basketindex_Order_3 <- desiredOrder(CMS_Daily.index.df[1, ], desiredIndex_3)
basketDailylogr_ts_3 <- generateLogr(CMS_Daily.ts, basketindex_Order_3)

print(paste0("Log Return Generation for ", desiredIndex_1, " is DONE!"))
print(paste0("Log Return Generation for ", desiredIndex_2, " is DONE!"))
print(paste0("Log Return Generation for ", desiredIndex_3, " is DONE!"))

```

# Calculate the Correction of `r desiredIndex_1`

```{r}
corMatrix <- round(cor(basketDailylogr_ts_1), digits = 2)
```

## corrplot to `r desiredIndex_1`

```{r}
library(corrplot)
re = cor(basketDailylogr_ts_1, use = "complete.obs")
corrplot(re)
```

## most correlated to `r desiredIndex_1`

```{r}
mostCorrelated <- corMatrix[1, ]
mostCorrelated[order(mostCorrelated, decreasing = TRUE)][1:30]
```

--------------------------------------------------------------------------------

# Calculate the Correction of `r desiredIndex_2`

```{r}
corMatrix <- round(cor(basketDailylogr_ts_2), digits = 2)
```

## corrplot to `r desiredIndex_2`

```{r}
library(corrplot)
re = cor(basketDailylogr_ts_2, use = "complete.obs")
corrplot(re)
```

## most correlated to `r desiredIndex_2`

```{r}
mostCorrelated <- corMatrix[1, ]
mostCorrelated[order(mostCorrelated, decreasing = TRUE)][1:30]
```

--------------------------------------------------------------------------------

# Calculate the Correction of `r desiredIndex_3`

```{r}
corMatrix <- round(cor(basketDailylogr_ts_3), digits = 2)
```

## corrplot to `r desiredIndex_3`

```{r}
library(corrplot)
re = cor(basketDailylogr_ts_3, use = "complete.obs")
corrplot(re)
```

## most correlated to `r desiredIndex_3`

```{r}
mostCorrelated <- corMatrix[1, ]
mostCorrelated[order(mostCorrelated, decreasing = TRUE)][1:30]
```