---
title: "SCM RELATED"
#author: "CHENRUJIE"
#date: "2022年7月13日"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: spacelab
---

```{r setup, include=FALSE}
#Rmarkdown Global Setup--------------------------------------------------
library(knitr)
library(readr)
library(readxl)
library(mFilter)
library(zoo)
library(xts)
library(ggplot2)
library(ggpubr)
library(timeDate)
library(timeSeries)
library(ghyp)
library(fBasics)
library(fExtremes)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      fig.width = 14,
                      fig.height = 10)

#Global Enviornment Setup---------------------------------------------------
library(knitr)
knitr::opts_chunk$set(fig.width = 14,
                      fig.height = 6)
H <- new.env() #Enviornment to store variabels.
H$ref_TD.hour <- c("SCM_60", "AU0_60", "PG0_60", "EB0_60", "FU0_60", "TA0_60", "PP0_60", "L0_60", "V0_60", "LUM_60", "RU0_60")
H$ref_TD.hour.text <- c("INE CRUDE Major 60 min", "SHFE GOLD Major 60", "DCE Patrol Gas Major 60 min", "CZCE EB Major 60 min", "SHFE Fuel Major 60 min",  "CZCE Purified Terephthalic Acid Major 60",  "DCE PP Major 60 min", "SHFE LASTIC Major 60", "DCE PVC Major 60 min", "INE LOW SULFUR FUEL Major 60 min", "SHFE RUBBER Major 60 min")
H$ref_TD.hour.bk <- H$ref_TD.hour
H$ref_TD <- c("SCM", "AU0", "PG0", "EB0", "FU0", "TA0", "PP0", "L0", "V0", "LUM", "RU0")
H$ref_TD.text <- c("INE CRUDE Futures", "SHFE GOLD Futures", "DCE Patrol Gas Futures", "CZCE EB Futures", "SHFE FUEL Futures", "CZCE Purified Terephthalic Acid Futures", "DCE PP Futures", "SHFE LASTIC Futures", "DCE PVC Futures", "INE LOW SULFUR FUEL Futures", "SHFE RUBBER Futures")
H$wd_ind <- paste(format(Sys.Date() - months(1), "%Y-%m"), format(Sys.Date(), "%Y-%m"), sep = "/")
H$globalWD <- file.path("~/PRO80")
H$globalWD.DATA <- file.path(H$globalWD, "DATA")
```

TRADING SCORES
==================================================

```{r General Preparation Process}
#Functions.--------------------------------------
#Function to read from excel file and process with hodrick prescott filter.
H$read_xls_hpf <- function(contract_name){
  #Read Excel File Data.
  TD.read <- read_excel(file.path(H$globalWD.DATA, paste0(contract_name, ".xls")),
                        col_types = c("text", "text", "date",
                                      "numeric", "numeric", "numeric", 
                                      "numeric", "numeric", "numeric", 
                                      "numeric", "numeric", "numeric"),
                        col_names = TRUE
  )
  colnames(TD.read) <- c(paste0(contract_name, "Code"),
                         paste0(contract_name, "Contract"),
                         paste0(contract_name, "Date"),
                         paste0(contract_name, "Open"),
                         paste0(contract_name, "High"),
                         paste0(contract_name, "Low"),
                         paste0(contract_name, "Close"),
                         paste0(contract_name, "Chg"),
                         paste0(contract_name, "RateofChg"),
                         paste0(contract_name, "Vol"),
                         paste0(contract_name, "Amn"),
                         paste0(contract_name, "Settle"))
  TD.read <- TD.read[, -12]
  TD.read.na <- na.omit(TD.read)
  #Return Dataframe without NA.
  close.HPF <- hpfilter(TD.read.na[[paste0(contract_name, "Close")]], freq=2419200, type=c("lambda"), drift = FALSE)
  return.output <- as.data.frame(TD.read.na[, 3])
  return.output <- cbind(return.output,
                         TD.read.na[, 7],
                         close.HPF$trend,
                         close.HPF$cycle)
  colnames(return.output) <- c(paste0(contract_name, "Date"),
                               paste0(contract_name, "Close"),
                               paste0(contract_name, "_hpft"),
                               paste0(contract_name, "_hpfc"))
  return(return.output)
}
H$read_xls_hpf2 <- function(contract_name){
  #Read Excel File Data.
  TD.read <- read_excel(file.path(H$globalWD.DATA, paste0(contract_name, ".xls")),
                        col_types = c("text", "text", "date",
                                      "numeric", "numeric", "numeric", 
                                      "numeric", "numeric", "numeric", 
                                      "numeric", "numeric"),
                        col_names = TRUE
  )
  colnames(TD.read) <- c(paste0(contract_name, "Code"),
                         paste0(contract_name, "Contract"),
                         paste0(contract_name, "Date"),
                         paste0(contract_name, "Open"),
                         paste0(contract_name, "High"),
                         paste0(contract_name, "Low"),
                         paste0(contract_name, "Close"),
                         paste0(contract_name, "Chg"),
                         paste0(contract_name, "RateofChg"),
                         paste0(contract_name, "Vol"),
                         paste0(contract_name, "Amn"))
  TD.read.na <- na.omit(TD.read)
  #Return Dataframe without NA.
  close.HPF <- hpfilter(TD.read.na[[paste0(contract_name, "Close")]], freq=2419200, type=c("lambda"), drift = FALSE)
  return.output <- as.data.frame(TD.read.na[, 3])
  return.output <- cbind(return.output,
                         TD.read.na[, 7],
                         close.HPF$trend,
                         close.HPF$cycle)
  colnames(return.output) <- c(paste0(contract_name, "Date"),
                               paste0(contract_name, "Close"),
                               paste0(contract_name, "_hpft"),
                               paste0(contract_name, "_hpfc"))
  return(return.output)
}

#Functions to Reading Daily Trade Data
H$read_daily <- function(ref_names){
  return.list <- list(NULL)
  for (i in 1:length(ref_names)){
  TD.read <- read.csv(paste0(H$globalWD, "/DailyTDs/", ref_names[i], "DailyTD.csv"))
  TD.read.xts <- xts(TD.read[, -1], order.by = as.Date(TD.read[, 1], format = "%Y-%m-%d"))
  return.list[i] <- list(TD.read.xts)
  names(return.list)[i] <- c(paste0(ref_names[i], "_hpf.xts"))
  }
  return(return.list)
}

#Processing.-------------------------------------
#Read Hourly Trade Data.
H$HourlyTD.List <- list(NULL)
for(i in 1:length(H$ref_TD.hour)){
  if(i==1 | i==10){
    H$HourlyTD.List[i]  <- list(H$read_xls_hpf2(H$ref_TD.hour[i]))
    names(H$HourlyTD.List)[i] <- paste0(H$ref_TD.hour[i], "_hpf")
  }else{
    H$HourlyTD.List[i]  <- list(H$read_xls_hpf(H$ref_TD.hour[i]))
    names(H$HourlyTD.List)[i] <- paste0(H$ref_TD.hour[i], "_hpf")
  }
}

#For XTS output.
H$HourlyTD.xts.List <- list(NULL)
H$HourlyTD.xts.List.wd <- list(NULL)
for(i in 1:length(H$ref_TD.hour)){
  H$HourlyTD.xts.List[i] <- list(xts(H$HourlyTD.List[[paste0(H$ref_TD.hour[i], "_hpf")]][, -1], 
                                order.by = H$HourlyTD.List[[paste0(H$ref_TD.hour[i], "_hpf")]][, 1]))
  names(H$HourlyTD.xts.List)[i] <- paste0(H$ref_TD.hour[i], "_hpf.xts")
  ##Windowing the Hourly Trade Data
  H$xh <- xts(H$HourlyTD.List[[paste0(H$ref_TD.hour[i], "_hpf")]][, -1], 
                                order.by = H$HourlyTD.List[[paste0(H$ref_TD.hour[i], "_hpf")]][, 1])
  H$HourlyTD.xts.List.wd[i] <- list(H$xh[H$wd_ind])
  names(H$HourlyTD.xts.List.wd)[i] <- paste0(H$ref_TD.hour[i], "_wd_hpf.xts")
}
#Read Daily Trade Data
H$DailyTD.xts.List <- list(NULL)
H$DailyTD.xts.List <- H$read_daily(H$ref_TD)

#SAVE for Hourly TD_All.
H$HourlyTD.xts.List.bk <- H$HourlyTD.xts.List
```

BUILD AT: `r Sys.time()`

Abbreviation:

GHD --> Generalized Hyperbolic Distribution

GPD --> Generalized Pareto Distribution

```{r Generate the FLAGs}
# Generate the flag according to results of hpfilter.===========================
library(formattable)
flagPlot <- function(dataset.df){
  
  sign_formatter <- formatter("span", style = x ~ ifelse(x > 0, style("background-color" = "black", color = "white"), 
                                                 style("background-color" = "white", color = "black")))
  sign_buildin <- color_bar("lightblue")
  sign_result <- color_tile("transparent", "orange")
  
  formattable(dataset.df, list(
    "SCM_60" = sign_buildin,
    "BU0_60" = sign_buildin,
    "PG0_60" = sign_buildin,
    "EB0_60" = sign_buildin,
    "FU0_60" = sign_buildin,
    "TA0_60" = sign_buildin,
    "PP0_60" = sign_buildin,
    "L0_60" = sign_buildin,
    "EG0_60" = sign_buildin,
    "MA0_60" = sign_buildin,
    "RU0_60" = sign_buildin,
    "TOTAL_COUNT" = sign_result
  ))
}

flagPlotarea <- function(dataset.df){
  above_formatter = color_bar("lightpink")
  below_formatter = color_bar("lightgreen")
  result_formatter = color_tile("transparent", "lightblue")
  formattable(dataset.df, list(
    area(row = 1, col = 1:11) ~ above_formatter,
    area(row = 2, col = 1:11) ~ below_formatter,
    area(col = 12) ~ result_formatter
  ))
}

# Creating the dataframe to contain ABOVEorBELOW FLAG.--------------------------

ABOVEorBELOW.df <- data.frame(matrix(nrow = 2, ncol = length(H$ref_TD)+1))
colnames(ABOVEorBELOW.df) <- c(H$ref_TD.hour, "TOTAL_COUNT")
rownames(ABOVEorBELOW.df) <- c("ABOVE_TREND", "BELOW_TREND")
ABOVEorBELOW.df[1, dim(ABOVEorBELOW.df)[2]] <- 0
ABOVEorBELOW.df[2, dim(ABOVEorBELOW.df)[2]] <- 0

# Counting the results.
for(i in 1:length(H$ref_TD.hour)){
  ind = H$ref_TD.hour[i]
  singleTD <- H$HourlyTD.xts.List[[i]]
  singleLast <- last(singleTD)
  singleX <- singleLast[dim(singleLast)[1], dim(singleLast)[2]]
  if(singleX >= 0){
    ABOVEorBELOW.df[1, ind] <- 1
    ABOVEorBELOW.df[2, ind] <- 0
    ABOVEorBELOW.df[1, dim(ABOVEorBELOW.df)[2]] <- ABOVEorBELOW.df[1, dim(ABOVEorBELOW.df)[2]] + 1
  }else if(singleX < 0){
    ABOVEorBELOW.df[1, ind] <- 0
    ABOVEorBELOW.df[2, ind] <- 1
    ABOVEorBELOW.df[2, dim(ABOVEorBELOW.df)[2]] <- ABOVEorBELOW.df[2, dim(ABOVEorBELOW.df)[2]] + 1
  }
}

# Creating the dataframe to contain UPorDOWN FLAG.------------------------------
UPorDOWN.df <- data.frame(matrix(nrow = 2, ncol = length(H$ref_TD)+1))
colnames(UPorDOWN.df) <- c(H$ref_TD.hour, "TOTAL_COUNT")
rownames(UPorDOWN.df) <- c("TREND_UP", "TREND_DOWN")
UPorDOWN.df[1, dim(UPorDOWN.df)[2]] <- 0
UPorDOWN.df[2, dim(UPorDOWN.df)[2]] <- 0

# Counting the results.
for(i in 1:length(H$ref_TD.hour)){
  ind = H$ref_TD.hour[i]
  singleTD <- H$HourlyTD.xts.List[[i]]
  singleLast_1 <- singleTD[dim(singleTD)[1]-1, ]
  singleLast <- last(singleTD)
  singleX <- as.numeric(singleLast[1, 2]) - as.numeric(singleLast_1[1, 2])
  if(singleX >= 0){
    UPorDOWN.df[1, ind] <- 1
    UPorDOWN.df[2, ind] <- 0
    UPorDOWN.df[1, dim(UPorDOWN.df)[2]] <- UPorDOWN.df[1, dim(UPorDOWN.df)[2]] + 1
  }else if(singleX < 0){
    UPorDOWN.df[1, ind] <- 0
    UPorDOWN.df[2, ind] <- 1
    UPorDOWN.df[2, dim(UPorDOWN.df)[2]] <- UPorDOWN.df[2, dim(UPorDOWN.df)[2]] + 1
  }
}

# Creating the dataframe to contain STRONGorWEAK FLAG.--------------------------
STRONGorWEAK.df <- data.frame(matrix(nrow = 2, ncol = length(H$ref_TD)+1))
colnames(STRONGorWEAK.df) <- c(H$ref_TD.hour, "TOTAL_COUNT")
rownames(STRONGorWEAK.df) <- c("STRONG", "WEAK")
STRONGorWEAK.df[1, dim(STRONGorWEAK.df)[2]] <- 0
STRONGorWEAK.df[2, dim(STRONGorWEAK.df)[2]] <- 0

# Counting the results.
for(i in 1:length(H$ref_TD.hour)){
  ind = H$ref_TD.hour[i]
  singleTD <- H$HourlyTD.xts.List[[i]]
  singleLast <- last(singleTD)
  singleDTD <- H$DailyTD.xts.List[[i]]
  singleDLast <- last(singleDTD)
  singleX <- as.numeric(singleLast[1, 2]) - as.numeric(singleDLast[1, 2])
  if(singleX >= 0){
    STRONGorWEAK.df[1, ind] <- 1
    STRONGorWEAK.df[2, ind] <- 0
    STRONGorWEAK.df[1, dim(STRONGorWEAK.df)[2]] <- STRONGorWEAK.df[1, dim(STRONGorWEAK.df)[2]] + 1
  }else if(singleX < 0){
    STRONGorWEAK.df[1, ind] <- 0
    STRONGorWEAK.df[2, ind] <- 1
    STRONGorWEAK.df[2, dim(STRONGorWEAK.df)[2]] <- STRONGorWEAK.df[2, dim(STRONGorWEAK.df)[2]] + 1
  }
}


# Creating the dataframe to contain TRADE FLAG.---------------------------------
FLAG.df <- data.frame(matrix(nrow = 2, ncol = length(H$ref_TD)+1))
colnames(FLAG.df) <- c(H$ref_TD.hour, "TOTAL_COUNT")
rownames(FLAG.df) <- c("LONG_FLAG", "SHORT_FLAG")
FLAG.df[1, dim(FLAG.df)[2]] <- 0
FLAG.df[2, dim(FLAG.df)[2]] <- 0

# Counting the results.
for(i in 1:length(H$ref_TD.hour)){
  ind = H$ref_TD.hour[i]
  singleX_long <- ABOVEorBELOW.df[1, i] + UPorDOWN.df[1, i] + STRONGorWEAK.df[1, i]
  singleX_short <- ABOVEorBELOW.df[2, i] + UPorDOWN.df[2, i] + STRONGorWEAK.df[2, i]
  if(singleX_long >= 2){
    FLAG.df[1, ind] <- 1
    FLAG.df[2, ind] <- 0
    FLAG.df[1, dim(FLAG.df)[2]] <- FLAG.df[1, dim(FLAG.df)[2]] + 1
  }else if(singleX_long < 2){
    FLAG.df[1, ind] <- 0
    FLAG.df[2, ind] <- 1
    FLAG.df[2, dim(FLAG.df)[2]] <- FLAG.df[2, dim(FLAG.df)[2]] + 1
  }
}
```

TRADING SCORES {.tabset .tabset-fade}
-------------------------------------

### ABOVE_or_BELOW

```{r}
flagPlotarea(ABOVEorBELOW.df)
```

### UP_or_DOWN

```{r}
flagPlotarea(UPorDOWN.df)
```

### STRONG_or_WEAK

```{r}
flagPlotarea(STRONGorWEAK.df)
```

### SHOW_FLAG

```{r}
flagPlotarea(FLAG.df)
```

INE CRUDE
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 1

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.SCM.xts <- H[["DailyTD.xts.List"]][["SCM_hpf.xts"]]
H$HourlyTD.xts.List$SCM_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$SCM_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.SCM.xts <- merge.xts(H$HourlyTD.xts.List$SCM_60_hpf.2.xts,
                                 H$DailyTD.SCM.xts,
                                 join = "left")
index(H$MixFreTD.SCM.xts) <- index(H$HourlyTD.xts.List$SCM_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.SCM.xts)[1], 
                          to = index(H$MixFreTD.SCM.xts)[dim(H$MixFreTD.SCM.xts)[1]], by = "week")
H$MixFreTD.SCM.gg <- ggplot(H$MixFreTD.SCM.xts, aes(x = as.factor(index(H$MixFreTD.SCM.xts)), group = 1)) +
  geom_line(aes(y = SCM_60Close)) + 
  geom_line(aes(y = SCM_60_hpft), colour = "red") + 
  geom_point(aes(y = SCM_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("SCM Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.SCM.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle
##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 25)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 60)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

GOLD
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 2

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.AU0.xts <- H[["DailyTD.xts.List"]][["AU0_hpf.xts"]]
H$HourlyTD.xts.List$AU0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$AU0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.AU0.xts <- merge.xts(H$HourlyTD.xts.List$AU0_60_hpf.2.xts,
                                 H$DailyTD.AU0.xts,
                                 join = "left")
index(H$MixFreTD.AU0.xts) <- index(H$HourlyTD.xts.List$AU0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.AU0.xts)[1], 
                          to = index(H$MixFreTD.AU0.xts)[dim(H$MixFreTD.AU0.xts)[1]], by = "week")
H$MixFreTD.AU0.gg <- ggplot(H$MixFreTD.AU0.xts, aes(x = as.factor(index(H$MixFreTD.AU0.xts)), group = 1)) +
  geom_line(aes(y = AU0_60Close)) + 
  geom_line(aes(y = AU0_60_hpft), colour = "red") + 
  geom_point(aes(y = AU0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("AU0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.AU0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.25, 0.50, 0.75, 0.85, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 5)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 15)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

PATROL GASS
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 3

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.PG0.xts <- H[["DailyTD.xts.List"]][["PG0_hpf.xts"]]
H$HourlyTD.xts.List$PG0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$PG0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.PG0.xts <- merge.xts(H$HourlyTD.xts.List$PG0_60_hpf.2.xts,
                                 H$DailyTD.PG0.xts,
                                 join = "left")
index(H$MixFreTD.PG0.xts) <- index(H$HourlyTD.xts.List$PG0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.PG0.xts)[1], 
                          to = index(H$MixFreTD.PG0.xts)[dim(H$MixFreTD.PG0.xts)[1]], by = "week")
H$MixFreTD.PG0.gg <- ggplot(H$MixFreTD.PG0.xts, aes(x = as.factor(index(H$MixFreTD.PG0.xts)), group = 1)) +
  geom_line(aes(y = PG0_60Close)) + 
  geom_line(aes(y = PG0_60_hpft), colour = "red") + 
  geom_point(aes(y = PG0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("PG0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.PG0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 250)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 300)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

EB
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 4

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.EB0.xts <- H[["DailyTD.xts.List"]][["EB0_hpf.xts"]]
H$HourlyTD.xts.List$EB0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$EB0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.EB0.xts <- merge.xts(H$HourlyTD.xts.List$EB0_60_hpf.2.xts,
                                 H$DailyTD.EB0.xts,
                                 join = "left")
index(H$MixFreTD.EB0.xts) <- index(H$HourlyTD.xts.List$EB0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.EB0.xts)[1], 
                          to = index(H$MixFreTD.EB0.xts)[dim(H$MixFreTD.EB0.xts)[1]], by = "week")
H$MixFreTD.EB0.gg <- ggplot(H$MixFreTD.EB0.xts, aes(x = as.factor(index(H$MixFreTD.EB0.xts)), group = 1)) +
  geom_line(aes(y = EB0_60Close)) + 
  geom_line(aes(y = EB0_60_hpft), colour = "red") + 
  geom_point(aes(y = EB0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("EB0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.EB0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.85, 0.90, 0.95, 0.99, 0.995, 0.999)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 300)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 1000)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

SHFE FUEL
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 5

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.FU0.xts <- H[["DailyTD.xts.List"]][["FU0_hpf.xts"]]
H$HourlyTD.xts.List$FU0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$FU0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.FU0.xts <- merge.xts(H$HourlyTD.xts.List$FU0_60_hpf.2.xts,
                                 H$DailyTD.FU0.xts,
                                 join = "left")
index(H$MixFreTD.FU0.xts) <- index(H$HourlyTD.xts.List$FU0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.FU0.xts)[1], 
                          to = index(H$MixFreTD.FU0.xts)[dim(H$MixFreTD.FU0.xts)[1]], by = "week")
H$MixFreTD.FU0.gg <- ggplot(H$MixFreTD.FU0.xts, aes(x = as.factor(index(H$MixFreTD.FU0.xts)), group = 1)) +
  geom_line(aes(y = FU0_60Close)) + 
  geom_line(aes(y = FU0_60_hpft), colour = "red") + 
  geom_point(aes(y = FU0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("FU0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.FU0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.50, 0.60, 0.70, 0.80, 0.90, 0.95)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 150)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 200)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

PTA
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 6

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.TA0.xts <- H[["DailyTD.xts.List"]][["TA0_hpf.xts"]]
H$HourlyTD.xts.List$TA0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$TA0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.TA0.xts <- merge.xts(H$HourlyTD.xts.List$TA0_60_hpf.2.xts,
                                 H$DailyTD.TA0.xts,
                                 join = "left")
index(H$MixFreTD.TA0.xts) <- index(H$HourlyTD.xts.List$TA0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.TA0.xts)[1], 
                          to = index(H$MixFreTD.TA0.xts)[dim(H$MixFreTD.TA0.xts)[1]], by = "week")
H$MixFreTD.TA0.gg <- ggplot(H$MixFreTD.TA0.xts, aes(x = as.factor(index(H$MixFreTD.TA0.xts)), group = 1)) +
  geom_line(aes(y = TA0_60Close)) + 
  geom_line(aes(y = TA0_60_hpft), colour = "red") + 
  geom_point(aes(y = TA0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("TA0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.TA0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 160)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 550)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

PP
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 7

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.PP0.xts <- H[["DailyTD.xts.List"]][["PP0_hpf.xts"]]
H$HourlyTD.xts.List$PP0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$PP0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.PP0.xts <- merge.xts(H$HourlyTD.xts.List$PP0_60_hpf.2.xts,
                                 H$DailyTD.PP0.xts,
                                 join = "left")
index(H$MixFreTD.PP0.xts) <- index(H$HourlyTD.xts.List$PP0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.PP0.xts)[1], 
                          to = index(H$MixFreTD.PP0.xts)[dim(H$MixFreTD.PP0.xts)[1]], by = "week")
H$MixFreTD.PP0.gg <- ggplot(H$MixFreTD.PP0.xts, aes(x = as.factor(index(H$MixFreTD.PP0.xts)), group = 1)) +
  geom_line(aes(y = PP0_60Close)) + 
  geom_line(aes(y = PP0_60_hpft), colour = "red") + 
  geom_point(aes(y = PP0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("PP0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.PP0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.80, 0.85, 0.90, 0.95, 0.99, 0.999)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 200)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 700)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

LASTIC
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 8

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.L0.xts <- H[["DailyTD.xts.List"]][["L0_hpf.xts"]]
H$HourlyTD.xts.List$L0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$L0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.L0.xts <- merge.xts(H$HourlyTD.xts.List$L0_60_hpf.2.xts,
                                 H$DailyTD.L0.xts,
                                 join = "left")
index(H$MixFreTD.L0.xts) <- index(H$HourlyTD.xts.List$L0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.L0.xts)[1], 
                          to = index(H$MixFreTD.L0.xts)[dim(H$MixFreTD.L0.xts)[1]], by = "week")
H$MixFreTD.L0.gg <- ggplot(H$MixFreTD.L0.xts, aes(x = as.factor(index(H$MixFreTD.L0.xts)), group = 1)) +
  geom_line(aes(y = L0_60Close)) + 
  geom_line(aes(y = L0_60_hpft), colour = "red") + 
  geom_point(aes(y = L0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("L0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.L0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 200)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 600)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

PVC
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 9

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.V0.xts <- H[["DailyTD.xts.List"]][["V0_hpf.xts"]]
H$HourlyTD.xts.List$V0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$V0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.V0.xts <- merge.xts(H$HourlyTD.xts.List$V0_60_hpf.2.xts,
                                 H$DailyTD.V0.xts,
                                 join = "left")
index(H$MixFreTD.V0.xts) <- index(H$HourlyTD.xts.List$V0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.V0.xts)[1], 
                          to = index(H$MixFreTD.V0.xts)[dim(H$MixFreTD.V0.xts)[1]], by = "week")
H$MixFreTD.V0.gg <- ggplot(H$MixFreTD.V0.xts, aes(x = as.factor(index(H$MixFreTD.V0.xts)), group = 1)) +
  geom_line(aes(y = V0_60Close)) + 
  geom_line(aes(y = V0_60_hpft), colour = "red") + 
  geom_point(aes(y = V0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("V0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.V0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 120)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 180)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

LOW SULFUR FUEL
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 10

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.LUM.xts <- H[["DailyTD.xts.List"]][["LUM_hpf.xts"]]
H$HourlyTD.xts.List$LUM_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$LUM_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.LUM.xts <- merge.xts(H$HourlyTD.xts.List$LUM_60_hpf.2.xts,
                                 H$DailyTD.LUM.xts,
                                 join = "left")
index(H$MixFreTD.LUM.xts) <- index(H$HourlyTD.xts.List$LUM_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.LUM.xts)[1], 
                          to = index(H$MixFreTD.LUM.xts)[dim(H$MixFreTD.LUM.xts)[1]], by = "week")
H$MixFreTD.LUM.gg <- ggplot(H$MixFreTD.LUM.xts, aes(x = as.factor(index(H$MixFreTD.LUM.xts)), group = 1)) +
  geom_line(aes(y = LUM_60Close)) + 
  geom_line(aes(y = LUM_60_hpft), colour = "red") + 
  geom_point(aes(y = LUM_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("LUM Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.LUM.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 200)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 300)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

RUBBER
==================================================

STATUS and DIST {.tabset .tabset-fade}
-------------------------------------

### STATUS

```{r, include=FALSE}
H$ind <- 11

#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, -3],
     main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```

```{r}
addSeries(H$HourlyTD.xts.List[[paste0(H$ref_TD.hour[H$ind], '_hpf.xts')]][, 3],
          main=paste0("Target 1: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### 30 DAYS

```{r, include = FALSE}
#xts output.
par(mai=c(0.5,0.5,0.5,0.5))
par(mfcol=c(1,1))
plot(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, -3],
     main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " Hodrict Presccot Filter"),observation.based = TRUE)
```


```{r}
addSeries(H$HourlyTD.xts.List.wd[[paste0(H$ref_TD.hour[H$ind], '_wd_hpf.xts')]][, 3],
          main=paste0("Target: ", H$ref_TD.hour.text[H$ind], " HPFC"))
```

### HvD STATUS

```{r}
#Changed into xts file.
H$DailyTD.RU0.xts <- H[["DailyTD.xts.List"]][["RU0_hpf.xts"]]
H$HourlyTD.xts.List$RU0_60_hpf.2.xts <- align.time(H$HourlyTD.xts.List$RU0_60_hpf.xts, 
                                                     n = 9 * 60*60)

#Align daily trade data with hourly trade data.
H$MixFreTD.RU0.xts <- merge.xts(H$HourlyTD.xts.List$RU0_60_hpf.2.xts,
                                 H$DailyTD.RU0.xts,
                                 join = "left")
index(H$MixFreTD.RU0.xts) <- index(H$HourlyTD.xts.List$RU0_60_hpf.xts)

#Try Using ggplot2 to show up the result.
H$x_label <- seq.POSIXt(from = index(H$MixFreTD.RU0.xts)[1], 
                          to = index(H$MixFreTD.RU0.xts)[dim(H$MixFreTD.RU0.xts)[1]], by = "week")
H$MixFreTD.RU0.gg <- ggplot(H$MixFreTD.RU0.xts, aes(x = as.factor(index(H$MixFreTD.RU0.xts)), group = 1)) +
  geom_line(aes(y = RU0_60Close)) + 
  geom_line(aes(y = RU0_60_hpft), colour = "red") + 
  geom_point(aes(y = RU0_hpft), colour = "blue", na.rm = TRUE) +
  scale_x_discrete(breaks = c(as.character(H$x_label)), labels = format(x = H$x_label, format = "%m%d")) +
  ggtitle("RU0 Hourly and Daily Trend.") + xlab("Trading Date")
H$MixFreTD.RU0.gg
```

### H_GHD

```{r, include=FALSE}
#Functions.======================================
#Functions to obtain timeSeries dataset.
H$DataSet_Fetch <- function(ref, suffix){
  attach(c(H$HourlyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$HourlyTD.xts.List))
  return(Return.get.ts)
}

#Preparing Dataset.==============================
H$DIST.Dataset.H <- H$DataSet_Fetch(H$ref_TD.hour[H$ind], "_hpf.xts")
H$DIST.Dataset.H.cycle <- na.omit(H$DIST.Dataset.H[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.H.ycycle <- H$DIST.Dataset.H.cycle[, c(paste0(H$ref_TD.hour[H$ind], "_hpfc"))]
H$DIST.H.ef <- density(H$DIST.H.ycycle)
#Density
H$DIST.H.ghdfit <- fit.ghypuv(H$DIST.H.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.H.ghddense <- dghyp(H$DIST.H.ef$x, H$DIST.H.ghdfit)
H$DIST.H.col.def <- c("black", "blue")
#VaR and ES
H$DIST.H.p <- seq(0.001, 0.05, 0.001)
H$DIST.H.VaR <- abs(qghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.emp.VaR <- abs(quantile(x = H$DIST.H.ycycle, probs = H$DIST.H.p))
H$DIST.H.ES <- abs(ESghyp(H$DIST.H.p, H$DIST.H.ghdfit))
H$DIST.H.obs.p <- ceiling(H$DIST.H.p * length(H$DIST.H.ycycle))
H$DIST.H.emp.ES <- sapply(H$DIST.H.obs.p, function(x) abs(mean(sort(c(H$DIST.H.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.H.ef, xlab = paste0(H$ref_TD.hour[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.H.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD.hour[H$ind], " Cycle"))
lines(H$DIST.H.ef$x, H$DIST.H.ghddense, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#VaR
plot(H$DIST.H.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.H.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.VaR)))
lines(seq(along = H$DIST.H.p), H$DIST.H.VaR, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

#ES
plot(H$DIST.H.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.H.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD.hour[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.H.p), labels = names(H$DIST.H.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.H.emp.ES)))
lines(1:length(H$DIST.H.p), H$DIST.H.ES, col = "blue")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.H.col.def, lty = 1)

par(mfcol = c(1,1))
```

### D_GHD

```{r, include=FALSE}
##Functions.=====================================
H$DataSet_Fetch_D <- function(ref, suffix){
  attach(c(H$DailyTD.xts.List))
  for(i in 1:min(length(ref), length(suffix))){
    Fetch.get <- get(paste0(ref[i], suffix[i]))
    if(i == 1){
      Return.get <- Fetch.get
    }else{
      Return.get <- merge.xts(Return.get, Fetch.get, join = "left")
    }
  }
  Return.get.ts <- timeSeries(Return.get, index(Return.get), format = "%Y-%m-%d %H:%M:%S")
  #Return desired objects
  detach(c(H$DailyTD.xts.List))
  return(Return.get.ts)
}

#Fetching Dataset.
H$DIST.Dataset.D <- H$DataSet_Fetch_D(H$ref_TD[H$ind], "_hpf.xts")
H$DIST.Dataset.D.cycle <- na.omit(H$DIST.Dataset.D[, c(paste0(H$ref_TD[H$ind], "_hpfc"))])
#Fitting Cycle to distribution function.
H$DIST.D.ycycle <- H$DIST.Dataset.D.cycle[, c(paste0(H$ref_TD[H$ind], "_hpfc"))]
H$DIST.D.ef <- density(H$DIST.D.ycycle)
#Density
H$DIST.D.ghdfit <- fit.ghypuv(H$DIST.D.ycycle, symmetric = FALSE, control = list(maxit = 1000))
H$DIST.D.ghddense <- dghyp(H$DIST.D.ef$x, H$DIST.D.ghdfit)
H$DIST.D.col.def <- c("black", "red")
#VaR and ES
H$DIST.D.p <- seq(0.001, 0.05, 0.001)
H$DIST.D.VaR <- abs(qghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.emp.VaR <- abs(quantile(x = H$DIST.D.ycycle, probs = H$DIST.D.p))
H$DIST.D.ES <- abs(ESghyp(H$DIST.D.p, H$DIST.D.ghdfit))
H$DIST.D.obs.p <- ceiling(H$DIST.D.p * length(H$DIST.D.ycycle))
H$DIST.D.emp.ES <- sapply(H$DIST.D.obs.p, function(x) abs(mean(sort(c(H$DIST.D.ycycle))[1:x])))
```

```{r}

par(mfcol = c(1, 3))
#Cycle
plot(H$DIST.D.ef, xlab = paste0(H$ref_TD[H$ind], " Cycle"), ylab = expression(f(x)), 
     ylim = c(0, max(H$DIST.D.ef$y*1.2)), main = paste0("Distribution of ", H$ref_TD[H$ind], " Cycle"))
lines(H$DIST.D.ef$x, H$DIST.D.ghddense, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#VaR
plot(H$DIST.D.emp.VaR, type = "l", xlab = "", ylab = "VaR", axes = FALSE, ylim = range(c(H$DIST.D.emp.VaR)),
     main = paste0("Value at Risk of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = seq(along = H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.VaR)))
lines(seq(along = H$DIST.D.p), H$DIST.D.VaR, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

#ES
plot(H$DIST.D.emp.ES, type = "l", xlab = "", ylab = "ES", axes = FALSE, ylim = range(c(H$DIST.D.emp.ES)), 
     main = paste0("Expected Shortfall of ", H$ref_TD[H$ind], " Cycle"))
box()
axis(1, at = 1:length(H$DIST.D.p), labels = names(H$DIST.D.emp.VaR), tick = FALSE)
axis(2, at = pretty(range(H$DIST.D.emp.ES)))
lines(1:length(H$DIST.D.p), H$DIST.D.ES, col = "red")
legend("topleft", legend = c("empirical", "GHD"), col = H$DIST.D.col.def, lty = 1)

par(mfcol = c(1,1))
```

### GPD_VaRnES

```{r, paged.print=TRUE}
H$GPD.H.cycle.tg1 <- H$DIST.H.ycycle
H$GPD.D.cycle.tg1 <- H$DIST.D.ycycle

##Defining probability parameters.
H$prob.ind <- c(0.75, 0.80, 0.85, 0.90, 0.95, 0.99)

##GPD
H$GPD.H.fit.tg1 <- gpdFit(H$GPD.H.cycle.tg1, u = 400)
H$GPD.H.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.H.fit.tg1, prob = H$prob.ind),
                           digits = 3)
H$GPD.D.fit.tg1 <- gpdFit(H$GPD.D.cycle.tg1, u = 2000)
H$GPD.D.VaRES.tg1 <- round(gpdRiskMeasures(H$GPD.D.fit.tg1, prob = H$prob.ind),
                           digits = 3)
##Output Table
H$GPD.H.VaRES.tg1.gg <- ggtexttable(H$GPD.H.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "pink", 
                                                                                   fill = "yellow",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.D.VaRES.tg1.gg <- ggtexttable(H$GPD.D.VaRES.tg1, 
                                    cols = c("Prob", "VaR", "ES"),
                                    theme = ttheme(colnames.style = colnames_style(color = "white", 
                                                                                   fill = "orange",
                                                                                   size = 20),
                                                   tbody.style = tbody_style(size = 20))
                                    )
H$GPD.H.VaRES.tg1.gg.output <- ggarrange(H$GPD.H.VaRES.tg1.gg, 
                                         H$GPD.D.VaRES.tg1.gg,
                                         ncol = 2, nrow = 1)
annotate_figure(H$GPD.H.VaRES.tg1.gg.output, top = text_grob(
  paste0("VaR and ES under GPD of ", H$ref_TD.hour[H$ind], " and ", H$ref_TD[H$ind], "."),
  size = 20, vjust = 5
  ))
```

COMPARE 
==================================================

```{r All Trading Datas, include=FALSE}
#Align all Trading Datas and giving output.
#Functions to align all trading Datas.
#Return with timeSeries files for convience of further analysis.
H$TD_align_all <- function(Major_ref, Align_ref){
  attach(c(H$HourlyTD.xts.List.bk))
  #Gets major trading data
  All.get <- get(paste0(Major_ref, "_hpf.xts"))
  index(All.get) <- strptime(index(All.get), "%Y-%m-%d %H:%M:%S", tz='UTC')
  #Align all trading data
  for(i in 1:length(Align_ref)){
    toAlign.get <- get(paste0(Align_ref[i], "_hpf.xts"))
    index(toAlign.get) <- strptime(index(toAlign.get), "%Y-%m-%d %H:%M:%S", tz='UTC')
    All.get <- merge.xts(All.get, toAlign.get, join = "left")
  }
  All.get.ts <- timeSeries(All.get, index(All.get), format = "%Y-%m-%d %H:%M:%S", tz='UTC')
  #Return desired objects
  detach(c(H$HourlyTD.xts.List.bk))
  return(All.get.ts)
}

#Processing--------------------------------------
#Align all to CN 10yr Treasury Futures Close Price
H$Major_ref <- H$ref_TD.hour.bk[2]
H$Align_ref <- H$ref_TD.hour.bk[c(-1, -2)]
#Process to get all Trade Data aligned.
H$Hourly_TD_All.ts <- H$TD_align_all(H$Major_ref, H$Align_ref)
H$output_ref <- c("All Trends", "All Cycles")

# Saving to files
if(!dir.exists("DEEPLEARN")){
  dir.create("DEEPLEARN")
}
write.csv(H$Hourly_TD_All.ts, "DEEPLEARN/hourly_all_scm_related.csv", col.names = TRUE)
H$ref_TD.hour.output.df <- rbind(H$ref_TD.hour, H$ref_TD.hour.text)
write.csv(H$ref_TD.hour.output.df, "DEEPLEARN/ref_hourly_scm_related.csv", row.names = FALSE)
```

COMPARE {.tabset .tabset-fade}
-------------------------------------

### TREND

```{r echo=FALSE}
#Functions to plot the reengineered data.
#Function 1 to use plot()
H$Reengineered_Dataset_Plot <- function(Reengineered_DS = timeSeries(NULL),
                                             emphasis.lwd = NULL,
                                             emphasis.lty = NULL){#Parameter for emphasis in plot.
  #Checking emphasis parameter.
  if(is.null(emphasis.lwd)){
    emphasis.lwd <- c(3, rep(1, dim(Reengineered_DS)[2]-1))
  }
  if(is.null(emphasis.lty)){
    emphasis.lty <- c(1, rep(3, dim(Reengineered_DS)[2]-1))
  }
  par(mai=c(0.5,0.5,0.5,0.5))
  par(mfcol=c(1,1))
  for(ig in 1:(dim(Reengineered_DS)[2]-1)){
    if(ig == 1){
      par(new = F)
      timeSeries::plot(Reengineered_DS[, ig], plot.type = c("single"), 
                       ann = FALSE, col = 1, lwd = emphasis.lwd[ig], lty = emphasis.lty[ig])
      grid()
      par(new = T)
      timeSeries::plot(Reengineered_DS[, ig+1], plot.type = c("single"), 
                       ann = FALSE, col = ig+1, yaxt = "n", xaxt = "n", 
                       axes = FALSE, lwd = emphasis.lwd[ig + 1], lty = emphasis.lty[ig + 1])
    }else{
      par(new = T)
      timeSeries::plot(Reengineered_DS[, ig+1], plot.type = c("single"), 
                       ann = FALSE, col = ig+1, yaxt = "n", xaxt = "n", 
                       axes = FALSE, lwd = emphasis.lwd[ig + 1], lty = emphasis.lty[ig + 1])
    }
  }
  mtext(paste0("FIGUER 1. ", colnames(Reengineered_DS)[1], " to ", 
               toString(colnames(Reengineered_DS)[-1]), "."), 
        side =3, ces = 1)
  legend("topleft", c(colnames(Reengineered_DS)), lty =1, 
         col = seq.int(1, dim(Reengineered_DS)[2]),
         lwd = emphasis.lwd)
}

H$Trends.Hourly_TD_All <- H$Hourly_TD_All.ts[, paste0(H$ref_TD.hour.bk[-1], "_hpft")]
H$Cycles.Hourly_TD_All <- H$Hourly_TD_All.ts[, paste0(H$ref_TD.hour.bk[-1], "_hpfc")]
H$ref_TD.hour.bk.lwd <- c(rep(7, 3), rep(4, 4), rep(5, 4))
H$ref_TD.hour.bk.lty <- c(rep(1, 3), rep(3, 4), rep(5, 4))

##Ploting.=======================================
H$Reengineered_Dataset_Plot(H$Trends.Hourly_TD_All, 
                            H$ref_TD.hour.bk.lwd, H$ref_TD.hour.bk.lwd)
```

### CYCLE_HISTOGRAM

```{r echo=FALSE}
##Functions for ggplot2.-------------------------
H$Histo_Graph <- function(data.DF, data.ind = NULL){
  ##Changing data frame into with Facets
  Histogram.DF <- NULL
  for (i in 1:length(data.ind)){
    Histogram.DF <- c(Histogram.DF, round(data.DF[, i], digits = 0))
  }
  Histogram.DF  <- cbind(Histogram.DF, rep(data.ind, each = dim(data.DF)[1]))
  Histogram.DF <- as.data.frame(Histogram.DF, stringsAsFactors = FALSE, make.names = FALSE)
  Histogram.DF[, 1] <- as.numeric(Histogram.DF[, 1])
  colnames(Histogram.DF) <- c("hpfc", "facet")
  #Current Step
  Histogram.DF.x1 <- NULL
  for (i in 1:length(data.ind)){
    Histogram.DF.x1 <- rbind(Histogram.DF.x1, Histogram.DF[dim(data.DF)[1]*i, ])
  }
  Histogram.DF.x1 <- as.data.frame(Histogram.DF.x1, make.names = FALSE)
  colnames(Histogram.DF.x1) <- c("close", "facet")
  #One Step Back
  Histogram.DF.x2 <- NULL
  for (i in 1:length(data.ind)){
    Histogram.DF.x2 <- rbind(Histogram.DF.x2, Histogram.DF[dim(data.DF)[1]*i - 1, ])
  }
  Histogram.DF.x2 <- as.data.frame(Histogram.DF.x2, make.names = FALSE)
  colnames(Histogram.DF.x2) <- c("close", "facet")
  #Two Steps Back
  Histogram.DF.x3 <- NULL
  for (i in 1:length(data.ind)){
    Histogram.DF.x3 <- rbind(Histogram.DF.x3, Histogram.DF[dim(data.DF)[1]*i - 2, ])
  }
  Histogram.DF.x3 <- as.data.frame(Histogram.DF.x3, make.names = FALSE)
  colnames(Histogram.DF.x3) <- c("close", "facet")

      
  ##Generating ggplot graphic.
  return.gg <- ggplot(Histogram.DF, aes(x = hpfc)) + 
    geom_histogram(binwidth = 5, fill = "white", colour = "black") +
    facet_grid(facet ~ .) +
    geom_point(data = Histogram.DF.x1, aes(x =close, y = 5), size = 4, alpha = 0.5) + 
    geom_point(data = Histogram.DF.x2, aes(x =close, y = 5), size = 2.5, alpha = 0.5) +
    geom_point(data = Histogram.DF.x3, aes(x =close, y = 5), size = 2, alpha = 0.5)

  return(return.gg)
}

##Ploting Histograms.----------------------------
#Normalized the dataset before ploting, SC contracts multiply by 10, while T contract multiply by 100.
H$dataset_for_plot <- data.frame(H$Cycles.Hourly_TD_All@.Data)
H$dataset_for_plot <- scale(H$dataset_for_plot) * 50
H$dataset_for_plot <- round(H$dataset_for_plot, digits = 0)

H$Histo.gg1 <- H$Histo_Graph(data.DF = H$dataset_for_plot, 
                             data.ind = H$ref_TD.hour.bk[-1])
H$Histo.gg1

```

CYCLES {data-height=800} 
==================================================

```{r echo=FALSE}
##Function to visualize the cycle.---------------
H$Cycles_Visualize_f3 <- function(Cycle_dataset, #Cycles
                              Major_id = 1){ #For Ploting Major curve
  #Setting ploting layout.
  par(mai=c(0.38,0.5,0.3,0.5))
  par(mfcol = c(2,1))
  #Ploting
    for(ig in 1:dim(Cycle_dataset)[2]){
      if(ig == dim(Cycle_dataset)[2]){
        par(new = F)
        timeSeries::plot(Cycle_dataset[, Major_id], plot.type = c("single"), ann = FALSE, 
                         col = Major_id)
        grid()
        par(new = T)
        timeSeries::plot(Cycle_dataset[, ig], plot.type = c("single"), 
                         ann = FALSE, col = ig, yaxt = "n", xaxt = "n")
        mtext(paste0("CYCLES VISUALIZING: ", 
                     Cycle_dataset@units[Major_id], " to ", 
                     Cycle_dataset@units[ig]), side = 3, cex = 1)
        legend("topleft", c(Cycle_dataset@units[Major_id], Cycle_dataset@units[ig]), 
               lty = 1, col= c(Major_id, ig))
        #Then plot layer shows all curves.
        for (ig2 in 1: dim(Cycle_dataset)[2]){
          if(ig2 == 1){
            par(new = F)
            timeSeries::plot(Cycle_dataset[, ig2], plot.type = c("single"), ann = FALSE, 
                             col = ig2, lwd = 2)
            grid()
          }else{
            par(new = T)
            timeSeries::plot(Cycle_dataset[, ig2], plot.type = c("single"), 
                             ann = FALSE, col = ig2, yaxt = "n", xaxt = "n")
          }
        }
        mtext(paste0("CYCLES VISUALIZING: ", Cycle_dataset@units[Major_id], 
                     " to All Cycles."), side = 3, cex = 1)
        legend("topleft", Cycle_dataset@units, lty = 1, col= seq.int(1, dim(Cycle_dataset)[2]))
      }else if(ig == 1){
        ##Plot the first 3 Colums together.
        par(new = F)
        timeSeries::plot(Cycle_dataset[, 1], plot.type = c("single"), ann = FALSE, col = 1, lwd = 2)
        grid()
        par(new = T)
        timeSeries::plot(Cycle_dataset[, 2], plot.type = c("single"), 
                         ann = FALSE, col = 2, yaxt = "n", xaxt = "n",
                         lwd = 1)
        par(new = T)
        timeSeries::plot(Cycle_dataset[, 3], plot.type = c("single"), 
                         ann = FALSE, col = 3, yaxt = "n", xaxt = "n",
                         lwd = 1)
        mtext(paste0("CYCLES VISUALIZING: ", 
                     Cycle_dataset@units[1], " to ", 
                     Cycle_dataset@units[2], " and ",
                     Cycle_dataset@units[3]), side = 3, cex = 1)
        legend("topleft", c(Cycle_dataset@units[1:3]), 
               lty = 1, col= c(1:3))
      }else{
        par(new = F)
        timeSeries::plot(Cycle_dataset[, Major_id], plot.type = c("single"), ann = FALSE, col = Major_id)
        grid()
        par(new = T)
        timeSeries::plot(Cycle_dataset[, ig], plot.type = c("single"), 
                         ann = FALSE, col = ig, yaxt = "n", xaxt = "n")
        mtext(paste0("CYCLES VISUALIZING: ", 
                     Cycle_dataset@units[Major_id], " to ", 
                     Cycle_dataset@units[ig]), side = 3, cex = 1)
        legend("topleft", c(Cycle_dataset@units[Major_id], Cycle_dataset@units[ig]), 
               lty = 1, col= c(Major_id, ig))
      }
    }
}

##Functions for ploting only 2 cycles
H$Cycles_Visualize_2 <- function(Cycle_dataset){ 
  #Setting ploting layout.
  par(mai=c(0.38,0.5,0.3,0.5))
  par(mfcol = c(1,1))
  #Ploting
  par(new = F)
  timeSeries::plot(Cycle_dataset[, 1], plot.type = c("single"), ann = FALSE, col = 1, lwd = 2)
  grid()
  par(new = T)
  timeSeries::plot(Cycle_dataset[, 2], plot.type = c("single"), 
                         ann = FALSE, col = 2, yaxt = "n", xaxt = "n",
                         lwd = 1)
  mtext(paste0("CYCLES VISUALIZING: ", 
                Cycle_dataset@units[1], " to ", 
                Cycle_dataset@units[2]), side = 3, cex = 1)
  legend("topleft", c(Cycle_dataset@units[1], Cycle_dataset@units[2]), 
               lty = 1, col= c(1, 2))
}


##Visualizing Hourly Cycle.----------------------
x <- dim(H$Cycles.Hourly_TD_All)[1]
H$Cycles_Visualize_f3(H$Cycles.Hourly_TD_All[seq(x-1000, x), ])
```

```{r Saving for finalProba project}
# Aggregate all the data
output_DATE = last(index(H$DailyTD.SCM.xts))

output_ABOVEorBELOW = data.frame(DATE = c(output_DATE, output_DATE),
                                 MODULE = c('ABOVEorBELOW', 'ABOVEorBELOW'),
                                 LABEL = c('ABOVE_TREND', 'BELOW_TREND'))
output_ABOVEorBELOW = cbind(output_ABOVEorBELOW, ABOVEorBELOW.df[1:(ncol(ABOVEorBELOW.df)-1)])

output_UPorDOWN = data.frame(DATE = c(output_DATE, output_DATE), 
                             MODULE = c('UPorDOWN', 'UPorDOWN'), 
                             LABEL = c('TREND_UP', 'TREND_DOWN'))
output_UPorDOWN = cbind(output_UPorDOWN, UPorDOWN.df[1:(ncol(UPorDOWN.df)-1)])

output_STRONGorWEAK = data.frame(DATE = c(output_DATE, output_DATE),
                                 MODULE = c('STRONGorWEAK', 'STRONGorWEAK'),
                                 LABEL = c('STRONG', 'WEAK'))
output_STRONGorWEAK = cbind(output_STRONGorWEAK, STRONGorWEAK.df[1:(ncol(STRONGorWEAK.df)-1)])

#output_FLAG = data.frame(DATE = c(output_DATE, output_DATE),
#                         MODULE = c('FLAG', 'FLAG'),
#                         LABEL = c('UP_FLAG', 'SHORT_FLAG'))
#output_FLAG = cbind(output_FLAG, FLAG.df[1:(ncol(FLAG.df)-1)])

output_PRO80 = output_ABOVEorBELOW
output_PRO80 = rbind(output_PRO80, output_UPorDOWN)
output_PRO80 = rbind(output_PRO80, output_STRONGorWEAK)
#output_PRO80 = rbind(output_PRO80, output_FLAG)

# Save to csv files for finalProba project.
savePath = file.path('~/finalProba/allProba')
write.csv(output_PRO80, file.path(savePath, 'pro80_SCM_related.csv'), col.names = TRUE)
```
