---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
#Rmarkdown Global Setup--------------------------------------------------
library(knitr)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      fig.width = 14,
                      fig.height = 10)
DLC <- new.env()
DLC$Time.start <- Sys.time()
```

RCNN for CYCLES
==================================================

Data Preparation Process

```{r Data Preparation}
library(imputeTS)
library(zoo)
library(xts)
##Functions.-------------------------------------
#Function to obtain return of dataframe.
DLC$return_DF <- function(dataset = as.data.frame(NULL), 
                          k = 1, #Order of difference
                          percentage = TRUE){ #X100 or not.
  lag0 <- dataset[-1:-k, ]
  lagk <- dataset[1:(dim(dataset)[1]-k), ]
  if(percentage == TRUE){
    return.R <- (lag0 - lagk) / lagk
    return.R <- return.R * 100
  }else{
    return.R <- (lag0 - lagk) / lagk
  }
  return(return.R)
}
##Lading Data into Memories.---------------------
#Import trends dataset from csv files.
DLC$Data_Loaded <- read.csv("DEEPLEARN/Cycles_Reengineered_Target1.csv", header = TRUE)

#Removing Missing Values.
#Subset the dataset after 2015-05-25 as China 10yr Treasury future started to trade at that date.
DLC$Data_Loaded.na <- subset.data.frame(DLC$Data_Loaded, as.Date(X) >= "2015-03-25")
DLC$Data_Loaded.na <- na.interpolation(DLC$Data_Loaded.na, option = "linear")

#Dataset Preparation
DLC$Model_Data.date <- as.Date(DLC$Data_Loaded.na[, 1])
DLC$Model_Data.nodate <- DLC$Data_Loaded.na[, -1]
#Return of cycles, percentage = TRUE
DLC$Model_Data.R <- DLC$return_DF(DLC$Model_Data.nodate, k = 1)

##Ploting results and outputs.-------------------
plot(DLC$Model_Data.R[, 1], type = "l", main = "Return of Lag 1 of cycles.", ylim = c(-500, 500))
```

From the Very Begining, Simple Network model is implemented into very simple Cycle dataset.

First Look at a neutral network model.

Inspired by iris project. The cycle of target, which was continuous, can be converted to discrete or even classes type. 

```{r First Look at a Neutral network model}
##Containing a 3 column dataset which are target, yield and currency respectively.
DLC$Sim_Net.Dataset <- DLC$Model_Data.nodate[, 1:3]
DLC$Sim_Net.Dataset.date <- DLC$Model_Data.date

##Obtaining training and testing dataset.
#Make testing dataset as the data of last 21 daily cycles.
DLC$Sim_Net.test.x <- DLC$Sim_Net.Dataset[(dim(DLC$Sim_Net.Dataset)[1] - 21 + 1):dim(DLC$Sim_Net.Dataset)[1], 2:3]
DLC$Sim_Net.test.y <- DLC$Sim_Net.Dataset[(dim(DLC$Sim_Net.Dataset)[1] - 21 + 1):dim(DLC$Sim_Net.Dataset)[1], 1]
DLC$Sim_Net.test.date <- DLC$Sim_Net.Dataset.date[(dim(DLC$Sim_Net.Dataset)[1] - 21 + 1):dim(DLC$Sim_Net.Dataset)[1]]
DLC$Sim_Net.test.label <- round((DLC$Sim_Net.test.y/100), digits = 0)
#And daily cycles before the last 21 days as the Training dataset.
DLC$Sim_Net.train.x <- DLC$Sim_Net.Dataset[1:(dim(DLC$Sim_Net.Dataset)[1] - 21), 2:3]
DLC$Sim_Net.train.y <- DLC$Sim_Net.Dataset[1:(dim(DLC$Sim_Net.Dataset)[1] - 21), 1]
DLC$Sim_Net.train.date <- DLC$Sim_Net.Dataset.date[1:(dim(DLC$Sim_Net.Dataset)[1] - 21)]
DLC$Sim_Net.train.label <- round((DLC$Sim_Net.train.y/100), digits = 0)

plot(DLC$Sim_Net.train.label,
     type = "h", main = "Target Plot", xlab = "Date", ylab = "Discrete")

```

```{r}
##Creating Network
##Loading Libraries.
library(keras)

DLC$units.c <- max(DLC$Sim_Net.train.label) - min(DLC$Sim_Net.train.label) + 1

##Network Architecture
DLC$Sim_Net.network <- keras_model_sequential() %>%
  layer_dense(units = 512, activation = "relu", input_shape = c(2)) %>%
  layer_dense(units = DLC$units.c, activation = "softmax")

##Compiling Step
DLC$Sim_Net.network %>% compile(
  optimizer = "rmsprop",
  loss = "categorical_crossentropy",
  metrics = c("accuracy")
)

##Reshaping the input dataset
DLC$Sim_Net.test.x <- array_reshape(as.matrix.data.frame(DLC$Sim_Net.test.x), c(dim(DLC$Sim_Net.test.x)[1], 2))
DLC$Sim_Net.train.x <- array_reshape(as.matrix.data.frame(DLC$Sim_Net.train.x), c(dim(DLC$Sim_Net.train.x)[1], 2))

##Categoricalized the labels.
DLC$Sim_Net.train.label <- to_categorical(DLC$Sim_Net.train.label, num_classes = DLC$units.c)
DLC$Sim_Net.test.label <- to_categorical(DLC$Sim_Net.test.label, num_classes = DLC$units.c)

##Fitting process.
DLC$Sim_Net.network %>% fit(DLC$Sim_Net.train.x, DLC$Sim_Net.train.label, epochs = 5, batch_size = 128)

##Prediction.
DLC$Sim_Net.network %>% predict_classes(DLC$Sim_Net.test.x)

```

But we achieve very low accuracy. In the following step, I will try concept of 3D tensor and implement a model of 3D tensor flow. The concept of 3D tensor to timeseries includes: The first axis is samples, which is the commordities I am trading, each type of commordity equals one sample; Second axis is the timesteps, which are the trading date either daily or hourly; Third axis is the features, which can be trading price, volume or others.

The the Convolutional Network is considered to be the model for dataset.

```{r Simple Convolutional Nework}
##Network Architecture
DLC$Convnet <- keras_model_sequential() %>%
  layer_conv_2d(filters = 32, kernel_size = c(1, 1), activation = "relu", input_shape = c(2, 1, 1))

##Dataset Preparation
##Containing a 3 column dataset which are target, yield and currency respectively.
DLC$Convnet.Dataset <- DLC$Model_Data.nodate[, 1:3]
DLC$Convnet.Dataset.date <- DLC$Model_Data.date

##Obtaining training and testing dataset.
#Make testing dataset as the data of last 21 daily cycles.
DLC$Convnet.test.x <- array(NA, c(21, 1, 2), dimnames = list(c(as.character(DLC$Convnet.test.date)), 
                                                          c("HPFC"), 
                                                          c(colnames(DLC$Convnet.Dataset)[2:3])))
  array(DLC$Convnet.Dataset[(dim(DLC$Convnet.Dataset)[1] - 21 + 1):dim(DLC$Convnet.Dataset)[1], 2])
  DLC$Sim_Net.Dataset[(dim(DLC$Convnet.Dataset)[1] - 21 + 1):dim(DLC$Convnet.Dataset)[1], 2:3]
DLC$Convnet.test.y <- DLC$Sim_Net.Dataset[(dim(DLC$Convnet.Dataset)[1] - 21 + 1):dim(DLC$Convnet.Dataset)[1], 1]
DLC$Convnet.test.date <- DLC$Convnet.Dataset.date[(dim(DLC$Convnet.Dataset)[1] - 21 + 1):dim(DLC$Convnet.Dataset)[1]]
DLC$Convnet.test.label <- round((DLC$Convnet.test.y/100), digits = 0)
#And daily cycles before the last 21 days as the Training dataset.
DLC$Convnet.train.x <- DLC$Convnet.Dataset[1:(dim(DLC$Convnet.Dataset)[1] - 21), 2:3]
DLC$Convnet.train.y <- DLC$Convnet.Dataset[1:(dim(DLC$Convnet.Dataset)[1] - 21), 1]
DLC$Convnet.train.date <- DLC$Convnet.Dataset.date[1:(dim(DLC$Convnet.Dataset)[1] - 21)]
DLC$Convnet.train.label <- round((DLC$Convnet.train.y/100), digits = 0)

##Reshaping the dataset
DLC$Convnet.test.x <- array_reshape(as.matrix.data.frame(DLC$Convnet.test.x), c(dim(DLC$Convnet.test.x)[1], 1))
DLC$Sim_Net.train.x <- array_reshape(as.matrix.data.frame(DLC$Sim_Net.train.x), c(dim(DLC$Sim_Net.train.x)[1], 2))

```

